### 2022-08-22 Bloods Data Sheet.Rmd
Export Data Sheet

@@

>>>>

```{r}
write.csv(main_df,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (22-08-2022).csv",row.names = FALSE)
```

@@

```{r}
main_df_PRE <- main_df%>%
  filter(!Time_Point %in% "2")%>%
  filter(!Time_Point %in% "3")

main_df <- main_df[main_df$cal_Cl <300,]
TRUNK_MAX_X <- TRUNK_MAX_X[TRUNK_MAX_X$TrunkAngle_X <10,]
```

### 2022-08-22 Draft Plots.Rmd
Export Data Sheet

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            #scale_y_continuous(name = "Chlorine \n",breaks = c(4,5,6,7,8,9,10), limits = c(4,10))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

>>>>

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Chlorine \n",breaks = c(90,100,110,120), limits = c(90,120))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
